\section{Related Work}

\subsection{Below the Surface}

The starting point for re-organizing the collection, creating aggregated datasets, and exploring overview data is the dataset downloadable in \textit{.csv} format on the Below the Surface project website. During the excavations around 700,000 objects were found, the dataset is a subset and contains around 20,000 objects that are digitally processed and rudimentary labeled. A separate data field description \footnote{https://belowthesurface.amsterdam/en/pagina/publicaties-en-datasets} file can be downloaded which further explains the controlled vocabulary used for the dataset.

\subsection{User Personas}

Defining the users is an important first step in developing a user-focused data system \cite{personas}. As our team did not have direct access to potential users, we developed three user personas to help guide our decision-making process for the website design.  

\subsubsection{Museum Curators}

Stephanie is a female professional museum curator, aged between 35 and 45.  She has a master's education in fine art and spends her days curating exhibitions for a local history museum in Amsterdam, the Netherlands.  She speaks English and Dutch.  Stephanie is good at networking and discovering new and interesting local history subjects.  She desires to find new stories, themes, and artifacts to be displayed in the local history museum.  Stephanie typically develops concepts by visiting other museums and exhibitions and building connections with other museum curators.  Stephanie has limited time available to research what artifacts to include in an exhibit. As a result, she values quicker methods of finding exhibit items.  Stephanie typically uses a desktop-based computer to access search engines, museum websites, and news websites.  She also arranges face-to-face meetings.

\subsubsection{Antique collectors}

Gerald is a male amateur antique collector, aged between 45 and 60.  He has a PhD in IT and is based in Europe.  He speaks English and has a growing collection of antiques from the 17th Century.  He has a desire to collect items that have some historic value, are from the 17th century, and have a unique visual appearance.  He collects his antiques in his spare time, so time spent searching for antiques is at a premium.  Gerald finds joy in hunting for antiques, especially using new ways to find antiques.  He sees's optimisation of searching for antiques as a benefit.  His main channels for searching are desktop research through search engines, auction houses, eBay and antique shops.

\subsubsection{Archaeologists}

Mădălina is a female archaeologist from Romania aged between 25 and 35.  She is currently in a PostDoc position researching building materials of the 18th century in European nations that border the North Sea.  She speaks English and German.  Kate is interested in the functional use of certain artifacts from different time periods within the 18th century, specifically building materials and techniques. Kate wants to find materials that have a specific function related to buildings.  Kate prefers to physically visit materials, archives and museums.  She is involved in excavations located around the North Sea coast.  She likes to spend time researching materials on her computer.  However, if she can make the search and selection of objects for viewing more efficient, she can spend more time analysing the findings that she does visit.  Kate's preferred channels for discovery are museum archives, search engines, and excavation project websites.

\subsection{Other websites}

Due to the user personas preferring websites similar to museum or archive websites, we searched for several others in the field to give us an idea.  We found 5 collections and museum archive websites that guided our design choices. We found that two sites had comparable layouts and search features found on the Below the surface website \footnote{https://www.vangoghmuseum.nl/nl/collectie?q=} \footnote{https://www.guggenheim.org/collection-online}.  The other three websites had additional features which enriched the search capabilities for users. Such as the ability to scroll down a collection based on the year \footnote{https://www.moma.org/calendar/exhibitions}, providing clear and simple visualizations corresponding to related data points \footnote{https://ourworldindata.org/how-many-animals-get-slaughtered-every-day}, and providing information on the numbers of tags and albums which have been highlighted by other users \footnote{https://www.fotozoektfamilie.nl}.  

As a result of the user personas, we decided that the website needed to be designed in a similar way to other websites from the field, give the ability to filter data based on object information, be a desktop-based website, and be available in English.